Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-02 writing/embedded_meta_learning.tex
Working on background

Our work builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- as well as work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}.

Other authors have proposed using a hyper network to guess parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}.

In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task.Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model, and also allows for remapping of behavior by meta-tasks.

>>>>

Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018} and continual learning, or more generally tools for avoiding catastrophic interference based on architectural innovations \citep[e.g.][]{Fernando2017, Rusu2016}, regularization terms \citep[e.g.][]{Kirkpatrick2016, Zenke2017} or external memory \citep[e.g.][]{Sprechmann2018}. There has also been interesting recent work on hybrid approaches, such as meta-learning in an online setting \citep{Finn2019}. Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than gradient descent \citep[e.g.][]{Wang2016a, Duan2016}. \par
Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications of it, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a}. This is related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Ba2016}. It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015}. \par 
There has also been some interest in task (or function) embeddings. In simultaneous work \citet{Achille2019} proposed computing embeddings for tasks from the Fisher information of the parameters in a model tuned (final layer only) on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Other recent work has suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. \par
